**Measuring Depression and Anxiety with 4 items? Adaptation of the PHQ-4 to increase its Sensitivity to Subclinical Variability**

### 2024-12-12 paper/4_WIP/manuscript.qmd
update

@@

      - name: "National Institute of Education"

@@

    documentmode: man
editor: 
  markdown: 
    wrap: 72

@@

The sample consists of 485 English-speaking participants (Mean age = 30.1 +- 10.1 [18, 73]; 50.3\% females) from the general population recruited via *Prolific*, a crowd-sourcing platform recognized for providing high quality data [@peer2022data]. The only inclusion criterion was a fluent proficiency in English to ensure that the task instructions would be well-understood. 
This study was approved by the 
<!-- Institutional Review Board **[Masked for Review]**. -->
NTU Institutional Review Board (NTU IRB-2022-187).
All participants provided their informed consent prior to participation and were incentivized after completing the study.

@@

The final sample included 836 participants (Mean age = 25.1 +- 11.3 [18, 76]; 73.8\% women).
This study was approved by the University of Sussex' Ethics Committee (ER/ASF25/4).

@@

The BDI-II [@beck1996beck] was used as a ground truth measure of depressive symptoms. It includes 21 items, each addressing a specific depression symptom and offering four response options scored from 0 to 3. Participants are instructed to select the option that best describes how they have felt over the past two weeks. 
The total score is calculated by summing the scores for all 21 items, with higher scores indicating greater severity of depressive symptoms.

The STAI-T5 [@zsido2020development] was used as a ground truth measure of anxiety. This abridged version of the STAI [@marteau1992development] includes 5 items rated on a 4-point Likert scale. Changes were made in the instructions from asking *"how participants feel right now"* to *"over the past 2 weeks"* to keep it consistent with the instructions of the PHQ-4 and BDI-II. A general score of anxiety was computed by averaging all the items.

@@

The original or refined version of the PHQ-4 was followed by the BDI-II, STAIT-5, IAS, and MAIA-2, presented in random order. The IAS and the MAIA-2 were included as part of another study focused on interoception, and were only used as part in this study of participation quality control.

@@

The linear regression predicting the BDI-II total score with the PHQ-4 depression score showed no interaction related to the PHQ-4 version ($\Delta Intercept_{\text{refined}} =  -0.13, 95\% CI[-1.73, 1.47], t(832) =  -0.16, p = 0.871 ; \Delta \beta_{\text{refined}} = -0.05, 95\% CI[-0.70, 0.60], t(832) = -0.15 , p = 0.883$), suggesting no differences in the relationship pattern between the two versions (see @fig-two).

Moreover, Bayesian *t*-tests (using *BayesFactor*'s `ttestBF()` function with default priors; @moreyrouder2024) comparing the BDI-II scores between the refined and the original version at each integer score (0, 1, 2, 3) yielded no evidence in favour of a significant difference (BF > 3). In other words, having the same score on the refined version as on the original version was related to the same outcome on the BDI-II.

@@

The linear regression predicting the STAI-5 general score with the PHQ-4 anxiety score showed no interaction related to the PHQ-4 version ($\Delta Intercept_{\text{refined}} =  -0.02, 95\% CI[-0.15, 0.11], t(832) =  -0.32, p = 0.750; \Delta \beta_{\text{refined}} = 0.01, 95\% CI[-0.03, 0.05], t(832) = 0.56 , p = 0.576$), suggesting no differences in the relationship pattern between the two versions.

>>>>

      - name: "University of Sussex"
        department:  "Sussex Centre for Consciousness Science"

@@

@@

    documentmode: jou

@@

The sample consists of 485 English-speaking participants (Mean age = 30.1 $\pm$ 10.1 [18, 73]; 50.3\% females) from the general population recruited via *Prolific*, a crowd-sourcing platform recognized for providing high quality data [@peer2022data]. The only inclusion criterion was a fluent proficiency in English to ensure that the task instructions would be well-understood. 
This study was approved by the 
<!-- Institutional Review Board **[Masked for Review]**. -->
NTU Institutional Review Board (NTU IRB-2022-187).
All participants provided their informed consent prior to participation and were incentivized after completing the study.

@@

The final sample included 836 participants (Mean age = 25.1 $\pm$ 11.3 [18, 76]; 73.8\% women).
This study was approved by the University of Sussex' Ethics Committee (ER/ASF25/4).

@@

Beck's Depression Inventory [BDI-II, @beck1996beck] was used as a ground truth measure of depressive symptoms. It includes 21 items, each addressing a specific depression symptom and offering four response options scored from 0 to 3. Participants are instructed to select the option that best describes how they have felt over the past two weeks. 
The total score is calculated by summing the scores for all 21 items, with higher scores indicating greater severity of depressive symptoms.

The short version of the State-Trait Anxiety Inventory [STAI-5, @zsido2020development] was used as a ground truth measure of anxiety. This abridged version of the STAI [@marteau1992development] includes 5 items rated on a 4-point Likert scale. Changes were made in the instructions from asking *"how participants feel right now"* to *"over the past 2 weeks"* to keep it consistent with the instructions of the PHQ-4 and BDI-II. A general score of anxiety was computed by averaging all the items.

@@

The original or refined version of the PHQ-4 was followed by the BDI-II, STAI-5, IAS, and MAIA-2, presented in random order. The IAS and the MAIA-2 were included as part of another study focused on interoception, and were only used as part in this study of participation quality control.

@@

The linear regression predicting the BDI-II total score with the PHQ-4 depression score showed no interaction related to the PHQ-4 version ($\Delta Intercept_{\text{refined}} =  -0.13,~95\%~CI~[-1.73, 1.47],~t(832) =  -0.16,~p = 0.871$; $\Delta \beta_{\text{refined}} = -0.05,~95\%~CI~[-0.70, 0.60],~t(832) = -0.15,~p = 0.883$), suggesting no differences in the relationship pattern between the two versions (see @fig-two).

Moreover, Bayesian *t*-tests [using *BayesFactor*'s `ttestBF()` function with default priors, @moreyrouder2024] comparing the BDI-II scores between the refined and the original version at each integer score (0, 1, 2, 3) yielded no evidence in favour of a significant difference (BF > 3). In other words, having the same score on the refined version as on the original version was related to the same outcome on the BDI-II.

@@

The linear regression predicting the STAI-5 general score with the PHQ-4 anxiety score showed no interaction related to the PHQ-4 version ($\Delta Intercept_{\text{refined}} =  -0.02,~95\%~CI~[-0.15, 0.11],~t(832) =  -0.32,~p = 0.750$; $\Delta \beta_{\text{refined}} = 0.01,~95\%~CI~[-0.03, 0.05],~t(832) = 0.56,~p = 0.576$), suggesting no differences in the relationship pattern between the two versions.
